---
title: "RA_SupervisedML"
author: "Ryan M. ALlen"
date: "April 27, 2018"
output: html_document
---

```{r data}
## Loading my Titanic Data
titanic <- read.csv("C:/Users/Ryan Allen/Documents/Regis/Work/Data/train.csv")
View(titanic)
titanic <- na.omit(titanic) ## omits any rows with na information
levels(titanic$Sex) <- c(1,0) ## 0 is male, 1 is female, knn cannot handle non-numeric data

##Cleaning the data
titanic$Name <- NULL
titanic$Ticket <- NULL
titanic$Cabin <- NULL
titanic$Embarked <- NULL
```

## Exploring the data
```{r explore}
## Exploring the data
library(dplyr)
library(ggvis)
library(class)
summary(titanic)

titanic %>% ggvis(~Survived,~Age, fill= ~Pclass) %>% layer_points()
titanic %>% ggvis(~Survived, ~Age, fill=~Sex) %>% layer_points()
```

## Setting our test and train data
```{r settingTest}
set.seed(3465)
ind <- sample(2, nrow(titanic), replace = TRUE, prob = c(0.8,0.2))

titanicTrain <- titanic[ind==1, 3:8]
titanicTest <- titanic[ind==2, 3:8]
titanicTrainLabels <- titanic[ind==1,2]
titanicTestLabels <- titanic[ind==2,2]
```

## Finding the k Nearest Neighbors of our training set
``` {r knn}
titanic_pred <- knn(train = titanicTrain, test = titanicTest, cl = titanicTrainLabels, k=2)

titanic_pred
```

## Evaluating our results
```{r results}
library(gmodels)

CrossTable(x=titanicTestLabels, y=titanic_pred, prop.chisq = FALSE)
```

### Analysis

My model correctly predicted 57 people would not survive (0 in the titanic_pred and 0 in the titanicTestLabels).
But I misidentified 24 peoople who did not survive as survivors.
I also also correctly identified 26 people as surviving, but had the 24 misidentified as not surviving that actually survived.
My model was better at predicting non-survival then it was at predicting survival.
